Molecular Gas \old{Dynamics} \new{Kinematics} of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-15 WRITEUP/diff.tex
update with mbox to strikethrough special symbols

% -------------------------------------- Final Edit Markup ----------------------------------
\usepackage[normalem]{ulem}
\usepackage{soul}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
\newcommand{\old}[1]{\textcolor{airforceblue}{\protect\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
% -----------------------------------------------------------------------------------------------

@@

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\%} inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\protect$>$0.27\petm{11}{8}\%} \new{$>$0.27\petm{0.11}{0.08}\%} which is higher
than the 
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

\old{\protect{
The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and
the lensed knots (see \Fig{CO21mom}).}}
\new{The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7, 
consistent with the results obtained by $uv$-plane fitting within the uncertainties. 
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
To model the complex spatial distribution of the line emission (\Fig{CO21mom}), we 
fit two independent Gaussians and find deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3.
Therefore, the emission is slightly resolved over $\sim$\,2 beams.
The lensed CO emission is unlikely to be distributed as Gaussians 
given the morphology seen in optical and \nir emission that were observed at higher resolution, 
i.e., the lensed emission of CO (without beam convolution) is more likely to have 
an annulus configuration enclosing a partially complete ``Einstein ring'' with 
structures along the arc 
and knots (see \Fig{CO21mom}). Nevertheless, the deconvolved source sizes and the
spatially offset blue wing compared to optical emission suggest that 
the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.}

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
\old{\protect{are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.}}
\new{\protect{are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.}}
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is with respect to \old{\protect{$z$=0.6537, which corresponds to the
dynamical center of the \bco line.}} \new{\protect{$z$=0.6541, which corresponds to the
line center of \bco line emission.}} The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

@@

\old{\protect{
Similar to previous studies of RXJ1131, where
differential lensing across the {\it HST}
$V$-, $I$-, and $H$-bands has been detected with a
magnification factor decreasing from 10.9 to 7.8 \citepalias{Claeskens06a},
the highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component.
This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
varies from 8.7 to 3.1 across the \bco line (\Tab{model}) and also partly due to a contribution from the companion in the redshifted velocity channels.}}
\new{\protect{Previous studies of RXJ1131 find evidence for differential lensing across 
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
Here, we find that the highly asymmetric \bco line profile is predominantly a result of 
differential lensing, where the redshifted emission is apparently much brighter than the
blueshifted component, as indicated by the difference in their magnification factor $(\mu_{\rm L})$, which
varies from 8.7 to 3.1 across the \bco line (\Tab{model}).
A secondary effect contributing to the asymmetry is caused by 
the CO emission in the companion in the redshifted velocity channels.}}
The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
% The difference in magnification factors between CO and optical-to-NIR
% may further indicate that the CO emitting region is more extended and/or
% has a spatial offset from the optical-to-NIR emission
% (\ie different positions and alignment relative to the caustics) given
% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5)
% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and
% the degeneracy between the intrinsic source size and the magnification factor.

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=0 0 30 0, clip, width=0.4\textwidth]{../Figures/veloGradient_markers}
\includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
\caption{Left: \old{\protect{Source-plane positions from best-fit \bco lens models are indicated with their associated uncertainties atop
the observed first moment map}}
\new{\protect{Source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown 
as markers color-coded by their velocities
atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}). }}
The contours are at steps of 50\,\kms. 
Despite the distorted first moment map in the image-plane due to differential lensing and beam smearing effects, the source-plane velocity gradient reconstructed from dynamical lens modeling suggests that
RXJ1131 is intrinsically a kinematically-ordered disk.
Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr \new{based on 
the reconstructed source-plane velocity gradient.}
Dashed line shows the best-fit ``rotation curve'' using an arctangent model.
The vertical error bars show the channel width for
each model and the horizontal error bars are the
1$\sigma$ uncertainties on the source-plane positions \new{along the major axis}.
 \label{fig:PV}}
\end{figure*}

@@

\input{table_mbb}
In the first model, we attempt to constrain the power-law index by including
the 24\,$\micron$ data. Based on the resulting posterior PDFs, we find an apparent
\new{IR luminosity (rest-frame 8\,$-$\,1000\,$\micron$) of 8.22\petm{2.75}{2.98}\E{12} \Lsun, a}
\fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
\old{\protect{3.81\petm{2.04}{1.92}\E{12}\,\Lsun}} \new{\protect{3.81\petm{1.92}{1.97}\E{12}\,\Lsun}}, and a
dust mass of 16\petm{5}{12}\E{8}\,\Msun, \new{all of which are} uncorrected for lensing \new{magnification}.
For the mass absorption coefficient, we adopt
$\kappa$\,=\,2.64\,m$^2$kg\pmOne at rest-frame 125.0\,$\micron$
\citep{Dunne03a}.
The dust mass uncertainty does not
include that of the absorption coefficient.

A fit including the MIR 24\,$\micron$ photometry
is likely an upper limit on the \fir luminosity due solely to \SF
in the AGN host galaxy.
% since the fit include contribution from the AGN (through power-law to MIR)
If we instead fit for a model excluding this constraint,
two major consequences are immediately apparent.
First, the power-law index is poorly-constrained (see \Tab{SED}).
Second, the steep power-law implies only a small contribution
from the power-law regime
to the total IR luminosity as compared to the graybody component.
Thus, the \fir luminosity in
this model should, in principle, correspond to a
lower limit on the cold dust emission.
Using the best-fit parameters
for this model, we find a total IR luminosity
\LIR (rest-frame 8\,$-$\,1000\,\micron) of \old{\protect{9.71\petm{6.14}{-6.05}\E{12}\,\Lsun}} \new{\protect{8.67\petm{5.27}{5.27}\E{12}\,\Lsun}},
a \fir luminosity \LFIR of \old{\protect{4.72\petm{2.54}{2.26}\E{12}\,\Lsun}} \new{\protect{4.24\petm{2.17}{2.00}\E{12}\,\Lsun}} and a
dust mass $M_{\rm dust}$ of \old{\protect{11\petm{5}{6}\E{8}\,\Msun}} \new{\protect{14\petm{5}{7}\E{8}\,\Msun}}, all of which are uncorrected for lensing.
Taken at face value, this implies an FIR-to-IR luminosity ratio
of \old{$\sim$58\pmm35\%} \new{$\sim$49\pmm38\%}.

@@

% -------
% WISE flux is slightly higher than the IRAC point, probably due to a smaller
% aperture used in IRAC extraction (both from archive).
\begin{figure}[!htbp]
\centering
\includegraphics[trim=5 5 5 5, clip, width=0.445\textwidth]{../Figures/FullSED_withMagphys}
\caption{SEDs of RXJ1131 at
$z_{\rm CO}$\eq0.654 and the lensing galaxy at $z$\eq0.295.
The photometry data (colored markers) are listed in \Tab{photometry}, except for those
shown in light blue circles, which are corrected for lensing magnification (see \Sec{SED}).
Assuming an MBB$+$power-law model for the thermal dust emission towards RXJ1131,
the dashed (dashed-dotted) line corresponds to the best-fit model
with (without) MIR constraint at 24\,$\micron$.
The solid black line shows the best-fit SED model with dust attenuation \old{\protect{(light blue solid line)
obtained using the \ncode{magphys} code.}}\new{\protect{obtained using the \ncode{magphys} code, whereas
the light blue solid line shows the unattenuated stellar emission. }}
\label{fig:SED}}
\end{figure}

@@

% ------------- gas fraction --------------
% Locally, the baryonic gas fraction for giant disks is ~7-10% (Leroy et al. 2008, Saintonge et al. 2011a), while
% at z~1.2 it increases to 34±5% and at z~2.3 to 44±6% (Tacconi
% et al. 2010, Daddi et al. 2010).
We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq\old{19\pmm5\%}\new{18\pmm4\%}
% , where the uncertainty is based on that of the gas mass.
and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\eq\old{\protect{32\petm{7}{12}\% for RXJ1131}}\new{\protect{34\pmm16\% for the merger system (i.e., RXJ1131 and companion)}}.
% The derived gas fraction of suggests that $\sim$70\% of the available baryonic mass has already been converted into stars.
Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $f_{\rm mol}$\ssim40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
% On the other hand,
% the baryonic gas mass fraction ranges from $\sim$10$-$30\% with an average of 0.21\pmm0.03 in normal ``star-forming'' galaxies at $z$\ssim0.4 \citep{Geach11a}, and $\sim$5 at $z$\ssim0 \citep{Saintonge11a}.
and from $f_\textrm{mol}$\ssim50\% to $\sim$5\% between the same redshift range for
``normal star-forming'' galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
\alphaco\eq4.6\,\alphaU to compute the molecular gas mass.}.
Both the dynamical and baryonic gas mass fractions of RXJ1131\new{+companion} are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2 %(e.g., \citealt{Lagos11a, Popping12a, Genzel15a})
which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.
%

@@

\old{\protect{One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
the central AGN, whereas this condition is not necessary for NLRs.
From an SDSS sample of $>$3800 quasars, \citet{Richards02a} find a
median of 97\kms and a dispersion of 269\,\kms in the distribution of
the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
that large offsets are uncommon. Nevertheless,
offsets as large as $\sim$\,500\,\kms have been observed in some cases.}}
%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption

>>>>

% -------------------------------------- Final Edit Markup ----------------------------------
\usepackage[normalem]{ulem}
\usepackage{soul}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
\newcommand{\old}[1]{\textcolor{airforceblue}{\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
% -----------------------------------------------------------------------------------------------

@@

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\%} inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\mbox{$>$0.27\petm{11}{8}\%}} \new{$>$0.27\petm{0.11}{0.08}\%} which is higher
than the
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

\old{
The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \mbox{\nir}
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and}
\old{\mbox{the lensed knots (see \Fig{CO21mom}).}}
\new{The deconvolved source size FWHM from fitting a single two-dimensional Gaussian
to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,
consistent with the results obtained by $uv$-plane fitting within the uncertainties.
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
To model the complex spatial distribution of the line emission (\Fig{CO21mom}), we
fit two independent Gaussians and find deconvolved source sizes of
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3.
Therefore, the emission is slightly resolved over $\sim$\,2 beams.
The lensed CO emission is unlikely to be distributed as Gaussians
given the morphology seen in optical and \nir emission that were observed at higher resolution,
i.e., the lensed emission of CO (without beam convolution) is more likely to have
an annulus configuration enclosing a partially complete ``Einstein ring'' with
structures along the arc
and knots (see \Fig{CO21mom}). Nevertheless, the deconvolved source sizes and the
spatially offset blue wing compared to optical emission suggest that
the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.}

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
\old{\mbox{are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.}}
\new{\mbox{are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.}}
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is with respect to \old{\mbox{$z$=0.6537, which corresponds to the
dynamical center of the \bco line.}} \new{\mbox{$z$=0.6541, which corresponds to the
line center of \bco line emission.}} The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

@@

\old{
Similar to previous studies of RXJ1131, where
differential lensing across the {\it HST}
$V$-, $I$-, and $H$-bands has been detected with a
magnification factor decreasing from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}},
the highly asymmetric \mbox{\bco} line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component.
This can be explained by the difference in magnification factor \mbox{$(\mu_{\rm L})$} which
varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
\new{\protect{Previous studies of RXJ1131 find evidence for differential lensing across
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
Here, we find that the highly asymmetric \bco line profile is predominantly a result of
differential lensing, where the redshifted emission is apparently much brighter than the
blueshifted component, as indicated by the difference in their magnification factor $(\mu_{\rm L})$, which
varies from 8.7 to 3.1 across the \bco line (\Tab{model}).
A secondary effect contributing to the asymmetry is caused by
the CO emission in the companion in the redshifted velocity channels.}}
The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
% The difference in magnification factors between CO and optical-to-NIR
% may further indicate that the CO emitting region is more extended and/or
% has a spatial offset from the optical-to-NIR emission
% (\ie different positions and alignment relative to the caustics) given
% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5)
% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and
% the degeneracy between the intrinsic source size and the magnification factor.

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=0 0 30 0, clip, width=0.4\textwidth]{../Figures/veloGradient_markers}
\includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
\caption{Left: \old{Source-plane positions from best-fit \mbox{\bco} lens models are indicated with their associated uncertainties atop
the observed first moment map}
\new{Source-plane positions obtained from the best-fit lens models (presented in \mbox{\Sec{lensmodel}}) are shown
as markers color-coded by their velocities
atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}). }
The contours are at steps of 50\,\kms.
Despite the distorted first moment map in the image-plane due to differential lensing and beam smearing effects, the source-plane velocity gradient reconstructed from dynamical lens modeling suggests that
RXJ1131 is intrinsically a kinematically-ordered disk.
Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr \new{based on
the reconstructed source-plane velocity gradient.}
Dashed line shows the best-fit ``rotation curve'' using an arctangent model.
The vertical error bars show the channel width for
each model and the horizontal error bars are the
1$\sigma$ uncertainties on the source-plane positions \new{along the major axis}.
 \label{fig:PV}}
\end{figure*}

@@

\input{table_mbb}
In the first model, we attempt to constrain the power-law index by including
the 24\,$\micron$ data. Based on the resulting posterior PDFs, we find an apparent
\new{IR luminosity (rest-frame 8\,$-$\,1000\,$\micron$) of 8.22\petm{2.75}{2.98}\E{12} \Lsun, a}
\fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
\old{\mbox{3.81\petm{2.04}{1.92}\E{12}\,\Lsun}} \new{\mbox{3.81\petm{1.92}{1.97}\E{12}\,\Lsun}}, and a
dust mass of 16\petm{5}{12}\E{8}\,\Msun, \new{all of which are} uncorrected for lensing \new{magnification}.
For the mass absorption coefficient, we adopt
$\kappa$\,=\,2.64\,m$^2$kg\pmOne at rest-frame 125.0\,$\micron$
\citep{Dunne03a}.
The dust mass uncertainty does not
include that of the absorption coefficient.

A fit including the MIR 24\,$\micron$ photometry
is likely an upper limit on the \fir luminosity due solely to \SF
in the AGN host galaxy.
% since the fit include contribution from the AGN (through power-law to MIR)
If we instead fit for a model excluding this constraint,
two major consequences are immediately apparent.
First, the power-law index is poorly-constrained (see \Tab{SED}).
Second, the steep power-law implies only a small contribution
from the power-law regime
to the total IR luminosity as compared to the graybody component.
Thus, the \fir luminosity in
this model should, in principle, correspond to a
lower limit on the cold dust emission.
Using the best-fit parameters
for this model, we find a total IR luminosity
\LIR (rest-frame 8\,$-$\,1000\,\micron) of \old{\mbox{9.71\petm{6.14}{-6.05}\E{12}\,\Lsun}} \new{\mbox{8.67\petm{5.27}{5.27}\E{12}\,\Lsun}},
a \fir luminosity \LFIR of \old{\mbox{4.72\petm{2.54}{2.26}\E{12}\,\Lsun}} \new{\mbox{4.24\petm{2.17}{2.00}\E{12}\,\Lsun}} and a
dust mass $M_{\rm dust}$ of \old{\mbox{11\petm{5}{6}\E{8}\,\Msun}} \new{\mbox{14\petm{5}{7}\E{8}\,\Msun}}, all of which are uncorrected for lensing.
Taken at face value, this implies an FIR-to-IR luminosity ratio
of \old{$\sim$58\pmm35\%} \new{$\sim$49\pmm38\%}.

@@

% -------
% WISE flux is slightly higher than the IRAC point, probably due to a smaller
% aperture used in IRAC extraction (both from archive).
\begin{figure}[!htbp]
\centering
\includegraphics[trim=5 5 5 5, clip, width=0.445\textwidth]{../Figures/FullSED_withMagphys}
\caption{SEDs of RXJ1131 at
$z_{\rm CO}$\eq0.654 and the lensing galaxy at $z$\eq0.295.
The photometry data (colored markers) are listed in \Tab{photometry}, except for those
shown in light blue circles, which are corrected for lensing magnification (see \Sec{SED}).
Assuming an MBB$+$power-law model for the thermal dust emission towards RXJ1131,
the dashed (dashed-dotted) line corresponds to the best-fit model
with (without) MIR constraint at 24\,$\micron$.
The solid black line shows the best-fit SED model with dust attenuation \old{\mbox{(light blue solid line)
obtained using the \ncode{magphys} code.}}\new{obtained using the \mbox{\ncode{magphys}} code, whereas
the light blue solid line shows the unattenuated stellar emission. }
\label{fig:SED}}
\end{figure}

@@

% ------------- gas fraction --------------
% Locally, the baryonic gas fraction for giant disks is ~7-10% (Leroy et al. 2008, Saintonge et al. 2011a), while
% at z~1.2 it increases to 34±5% and at z~2.3 to 44±6% (Tacconi
% et al. 2010, Daddi et al. 2010).
We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq\old{19\pmm5\%}\new{18\pmm4\%}
% , where the uncertainty is based on that of the gas mass.
and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\eq\old{\mbox{32\petm{7}{12}\% for RXJ1131}}\new{\mbox{34\pmm16\%} for the merger system (i.e., RXJ1131 and companion)}.
% The derived gas fraction of suggests that $\sim$70\% of the available baryonic mass has already been converted into stars.
Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $f_{\rm mol}$\ssim40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
% On the other hand,
% the baryonic gas mass fraction ranges from $\sim$10$-$30\% with an average of 0.21\pmm0.03 in normal ``star-forming'' galaxies at $z$\ssim0.4 \citep{Geach11a}, and $\sim$5 at $z$\ssim0 \citep{Saintonge11a}.
and from $f_\textrm{mol}$\ssim50\% to $\sim$5\% between the same redshift range for
``normal star-forming'' galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
\alphaco\eq4.6\,\alphaU to compute the molecular gas mass.}.
Both the dynamical and baryonic gas mass fractions of RXJ1131\new{+companion} are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2 %(e.g., \citealt{Lagos11a, Popping12a, Genzel15a})
which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.
%

@@

\old{One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
the central AGN, whereas this condition is not necessary for NLRs.
From an SDSS sample of $>$3800 quasars, \mbox{\citet{Richards02a}} find a
median of \mbox{97\kms} and a dispersion of 269\,\mbox{\kms} in the distribution of
the offset between \mbox{[Mg\,{\scriptsize II}] and [O\,{\scriptsize III}]} lines, suggesting
that large offsets are uncommon. Nevertheless,
offsets as large as $\sim$\,500\,\mbox{\kms} have been observed in some cases.}
%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
